---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HybridGIS

<!-- badges: start -->
<!-- badges: end -->

The HybridGIS project contains functions, analysis scripts and data for the NOSAMS hybrid gas ion source.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("blongworth/hgis")
```

Running `make` will download the NOSAMS results files if a connection to the NOSAMS file server is available. This currently uses an absolute path to the server of `/mnt/shared/USAMS/Results`. This should be converted to a URL, but until then, modify `RES_DIR` in `Makefile` to match it's location on your system. `make` will eventually run the analysis scripts as well. 

## Functions

Loading the package loads functions for flow calculation, efficiency, data import, data reduction and plotting.

```{r example}
library(HybridGIS)
```

```{r child='summary.Rmd'}
```